---
title: "Homework1"
author: "svs2130"
date: "9/19/2019"
output: github_document
---

```{r Problem_1}
library(tidyverse)

#Problem 1

set.seed(10)
df= tibble(
  random = rnorm(8),
  vec_logical = random > 0,
  vec_char = c("a", "b", "c", "d", "e", "f", "g", "h"),
  vec_factor = as.factor(c(1,2,3,1,1,2,3,2))
)

#Since the argument is numeric, we get a value
mean(pull(df, random)) #works
#Since the argument is logical, we get a value
mean(pull(df, vec_logical)) 
#works
#Since the argument isn't numeric or logical, the result is NA
mean(pull(df, vec_char)) 
#doesnt work
#Since the argument is neither numberic nor logical, the result is NA
mean(pull(df, vec_factor)) 
#doesnt work
mean(as.numeric(pull(df, vec_char))) 
#doesnt work because cannot take mean of characters
mean(as.numeric(pull(df, vec_factor)))
     
```



```{r Problem_1second}
# second code chunk
as.numeric(pull(df, vec_logical))*(pull(df, random))
as.factor(pull(df,vec_logical))*(pull(df, random))
as.numeric(as.factor(pull(df, vec_logical)))*(pull(df, random))
```


#Problem #2

Creating ggplots

```{r Problem2}

set.seed(1)
problem2_df = tibble(
  x = rnorm(500),
  y = rnorm(500),
  vec_logical = c(x + y > 1),
  vec_numeric = c(vec_logical),
  vec_factor = c(vec_logical)
)
```

* The number of rows in our data set is **`r nrow(problem2_df)`**.
* The number of columns in our dataset is **`r ncol(problem2_df)`**.
* The mean, median and Standard deviation of *x* are **`r mean(problem2_df$x)`, `r median(problem2_df$x)` and `r sd(problem2_df$x)`** respectively
* The proportion of cases for which the logical vector(x + y > 1) is true: **`r length(problem2_df$vec_logical[which(problem2_df$vec_logical == 'TRUE')]) / nrow(problem2_df)`**.

```{r scatter_plot}

```


